---
title: "R Project 1 - Hello R"
author: "Tabitha Vasquez"
date: "9/16/2020"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(Datasaurus Dozen data has 1846 rows, 3 variables, and the amount of columns depends on how many the user adds. The variables included in the data frame are if, ggplot, geom_point, theme_void, theme, and facet_wrap.)

### Exercise 2


```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

dino_data %>%
summarize(r = cor(x,y))
## # A tibble: 1 x 1
## r
## <dbl>
## 1 -0.0645

### Exercise 3

Plotting of star dataset

{r plot-star}
star_data <- datasaurus_dozen %>%
filter(dataset == "dino")

ggplot(data = start_data, mapping = aes(x = x, y = y)) +
geom_point()


Correlation of star dataset

{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

star_data %>%
summarize(r = cor(x,y))
## # A tibble: 1 x 1
## r
## <dbl>
## 1 -0.0645


### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

{r plot-circl}
circle_data <- datasaurus_dozen %>%
filter(dataset == "dino")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
geom_point()

{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

circle_data %>%
summarize(r = cor(x,y))
## # A tibble: 1 x 1
## r
## <dbl>
## 1 -0.0645



### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)